---
title: "CyVerse_Workflow_Notes"
author: "stribling"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##### General set-up & workflow for shared data, analyses, and coding for the forest fragmentation working group



###### Overall goal: Store all shared data online, develop code in a shared version-control workspace, and run code & analyses on shared data using cloud computing




#### **Data storage:**
**We can store data in a common folder in [CyVerse](www.cyverse.org)**

* Grace's shared folder is our current data home: "/iplant/home/mgracemcleod/Forest_Fragments/Data/"
* Our Team for this forest fragmentation working group is **"Forest Fragments"**

**Data notes & questions**

* I think (?) spatial shapefiles need to be stored unzipped within cyverse in order to access the files within the Cyverse's RStudio docker ("Rocker")
* It looks like we need **all** the multi-part files in order for R/Rocker to sucessfully read in a .shp file.
* What needs/issues does this generate for data storage?
      + How do we best manage multi-part shapefiles?
      + Does storing a bunch of files in Grace's folder use up all her storage space? If so, how can we share the             storage burden? Shareing with a "Team" sounds like the right solution, but I'm not currently able to share            with our Team.


#### **Code development:**
**We can store and edit code on Github, using a shared group repo, ["forest_frag"](https://github.com/stribstrib/forest_frag).**

* We can integrate the github repo with RStudio on personal computers or within CyVerse's RStudio ("Rocker"). 
  + This allows us to pull the most up-to-date code, edit it, and push code back to main repository. 
  + Version control within github allows us to "back up" and find old versions of code if we need to.    

**Coding notes & questions**

* Jenny Bryan's [Happy Git and GitHub for the useR](https://happygitwithr.com/) is a great resource for getting your RStudio fully integrated with GitHub.  
* It looks like we need **all** the multi-part files in order for R/Rocker to sucessfully read in a .shp file.
* What needs/issues does this generate for coding?
      + How do we best manage multi-part shapefiles?
      + Does storing a bunch of files in Grace's folder use up all her storage space? If so, how can we share the             storage burden? Shareing with a "Team" sounds like the right solution, but I'm not currently able to share            with our Team.

------------------------------------------

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
